\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{comment}

\begin{document}
\name{\huge Tam Le}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    713.935.5837       \hfill \url{https://www.linkedin.com/in/tamtale
    } \\
    \noindent tamtale@gmail.com  \hfill
    23 Sunset Boulevard, Houston, TX 77005

    \section{\mysidestyle Education}

    \textbf{Rice University}, Houston, TX \vspace{1mm}\\
    \textsl{B.S., Computer Science} \hfill \textbf{Aug 2016 -- May 2020} \vspace{1mm}\\
    \textsl{GPA: } 4.0 

\section{\mysidestyle Experience}

\textbf{Facebook, Inc.} \vspace{2mm}\\\vspace{1mm}%
\textsl{Software Engineering Intern} \hfill \textbf{May 2019 - Aug 2019}
\begin{itemize}
    \item Implemented reusable design components for mobile site with Hack, CSS and Javascript to reach parity with native iOS and Android platforms.
    \item Added autocomplete, syntax highlighting and code formatting to internal, browser-based Hack editor for NT, used by over 200 engineers monthly.
    \item Improved support tooling for internal feedback group with Hack scripts to decrease response time for support questions. 
    
\end{itemize}

\textbf{Rice University} \vspace{2mm}\\\vspace{1mm}%
\textsl{Teaching Assistant} \hfill \textbf{Jan 2019 - May 2019}
\begin{itemize}
    \item COMP 322 (Fundamentals of Parallel Programming) - Graded assignments, held office hours,
     and answered questions on the course forum.
     Contributed to Python script to automate data-entry for grading.
    
\end{itemize}

\textbf{JPMorgan Chase \& Co.}, Houston, TX \vspace{2mm}\\\vspace{1mm}%
\textsl{Software Engineering Intern} \hfill \textbf{June 2018 - Aug 2018}
\begin{itemize}
    \item Led a team of 4 interns in designing and developing an internal, CloudFoundry-hosted web application with React, Spring Boot, and MariaDB to enhance training experience for 700 technicians through ``gamified learning".
    \item Prepared a Jira board and wrote comprehensive Javadoc and Swagger documentation to migrate the project to a full-time team.
    \item Helped host training sessions for interns and full time employees in firmwide initiative to shift teams to agile development.
\end{itemize}

\textbf{Sri Academic Services}, Houston, TX \vspace{2mm}\\\vspace{1mm}%
\textsl{Private Tutor} \hfill \textbf{Aug 2016 - Dec 2016}
\begin{itemize}
    \item Tutored one-on-one high school students in the Houston area in Computer Science, Math, and Economics.
\end{itemize}

\begin{comment}
\textbf{Fishburn Violin Shop}, Tomball, TX \vspace{2mm}\\\vspace{1mm}%
\textsl{Sales Associate} \hfill \textbf{Aug 2015 -
Aug 2016}
\begin{itemize}
    \item Worked in a sales team of five at a local violin shop servicing six school districts in the northwest Houston area.
    \item Helped maintain rental logs for over 2,000 contracted customers, organized deliveries of rental instruments to public schools, assisted customers with instrument maintenance and repair.
\end{itemize}
\end{comment}
\vspace{1mm}%

\section{\mysidestyle Skills}

\emph{Languages}: Java, Hack, Javascript, Python, Scala, C\\

\section{\mysidestyle Projects}

\textbf{Morse Code Interpreter}---Worked in a team of 4 with a Tiva C microcontroller to implement a light-sensor based morse code interpreter to facilitate ``learning by doing" for morse code enthusiasts.
\textbf{Jam Interpreter}---Built an interpreter over the course of a semester in Java for Jam, a small functional language with some imperative constructs. 
Progressively added language features like static typechecking, continuation passing and storage limitation with a virtual heap.

\section{\mysidestyle Other\\ Activities}
\textbf{Vietnamese Student Association} \hfill \textbf{Aug 2016-Present}
\begin{itemize}
    \item Worked with other students on campus to host cultural and community outreach events.
    \item Helped organize and gave a workshop for the annual College Leadership Workshop for high school students in the Houston Area.
\end{itemize}



\end{resume}
\end{document}
